Blocking-resistant communication\\through domain fronting

### 2014-07-22 docs/meek.tex
Use my NoHyper macro.

A technique known as OSS~\cite{oss} (for
``online scanning service'') bounces data
through third-party web services that are capable of making HTTP requests.
For example, a censored client may ask a translation service to
translate a web page at \begin{NoHyper}\url{http://proxy.example.com/...}\end{NoHyper},
where ``\begin{NoHyper}\url{...}\end{NoHyper}''
stands for the data payload that the client wishes to send---data are embedded in the URL.
Simply by making the HTTP request, the service sends the client's message.
The client cannot rely on being able to receive the response to its message in an HTTP response,
because online scanning services do not in general
return unmodified the contents of the page they are ordered to retrieve.
The translation service, for example, returns the page in another language.
For this reason, the server sends a response message by making
another reflected HTTP request back to the client, through the same OSS or a different one.
The need for the client to receive a connection means that OSS has the same problem with NAT that flash proxy does.
The NAT aspect is the most important way in which our work improves on OSS.
App Engine is effectively an unblockable OSS that we fully control.
We can ensure that reflected HTTP bodies are unmodified, and therefore use them to carry traffic
without having to connect to the client.

@@

CloudTransport~\cite{cloudtransport} uses cloud storage, for example Amazon~S3,
as a communication channel by encoding sends and receives as reads and writes to shared remote files.
CloudTransport has much in common with domain fronting:
it hides the true endpoint of a communication with HTTPS,
and sends traffic through a domain with high collateral damage.
In CloudTransport, the hidden destination, which is a storage bucket name rather than a domain,
is hidden in the path rather than the Host header.
For example, in an example S3 URL
\begin{NoHyper}\url{https://s3.amazonaws.com/bucketname/filename}\end{NoHyper},
the censor only gets to ``see'' the generic domain part, \begin{NoHyper}\url{s3.amazonaws.com}\end{NoHyper}.
The path component \begin{NoHyper}\url{/bucketname/filename}\end{NoHyper},
which would reveal that CloudTransport is being used,
cannot be used for blocking because it is encrypted in HTTPS.

>>>>

A technique known as OSS~\cite{oss} (for
``online scanning service'') bounces data
through third-party web services that are capable of making HTTP requests.
For example, a censored client may ask a translation service to
translate a web page at \urll{http://proxy.example.com/...},
where ``\urll{...}''
stands for the data payload that the client wishes to send---data are embedded in the URL.
Simply by making the HTTP request, the service sends the client's message.
The client cannot rely on being able to receive the response to its message in an HTTP response,
because online scanning services do not in general
return unmodified the contents of the page they are ordered to retrieve.
The translation service, for example, returns the page in another language.
For this reason, the server sends a response message by making
another reflected HTTP request back to the client, through the same OSS or a different one.
The need for the client to receive a connection means that OSS has the same problem with NAT that flash proxy does.
The NAT aspect is the most important way in which our work improves on OSS.
App Engine is effectively an unblockable OSS that we fully control.
We can ensure that reflected HTTP bodies are unmodified, and therefore use them to carry traffic
without having to connect to the client.

@@

CloudTransport~\cite{cloudtransport} uses cloud storage, for example Amazon~S3,
as a communication channel by encoding sends and receives as reads and writes to shared remote files.
CloudTransport has much in common with domain fronting:
it hides the true endpoint of a communication with HTTPS,
and sends traffic through a domain with high collateral damage.
In CloudTransport, the hidden destination, which is a storage bucket name rather than a domain,
is hidden in the path rather than the Host header.
For example, in an example S3 URL
\urll{https://s3.amazonaws.com/bucketname/filename},
the censor only gets to ``see'' the generic domain part, \urll{s3.amazonaws.com}.
The path component \urll{/bucketname/filename},
which would reveal that CloudTransport is being used,
cannot be used for blocking because it is encrypted in HTTPS.
